<!-- Working with additional customisation techniques -->

<!-- Table of contents -->
---
title: "Investment Report"
output: 
  html_document:
    toc: true
date: "`r format(Sys.time(), '%d %B %Y')`"
---

<!-- Depth refers to how many # items for the headers that the TOC reviews -->
---
title: "Investment Report"
output: 
  html_document:
    toc: true
    toc_depth: 3
date: "`r format(Sys.time(), '%d %B %Y')`"
---

<!-- Adding a parameter to the report -->
---
title: "Investment Report"
output: 
  html_document:
    toc: true
    toc_float: true
date: "`r format(Sys.time(), '%d %B %Y')`"
params:
  country: Brazil 
---

<!-- Using the parameter in the report -->
```{r country-investment-projects}
country_investment_projects <- investment_services_projects %>%
  filter(country == params$country) 

ggplot(country_investment_projects, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  )
```
<!-- Parameter can be added to the title of the report -->
---
title: "Investment Report for Projects in `r params$country`"
output: 
  html_document:
    toc: true
    toc_float: true
date: "`r format(Sys.time(), '%d %B %Y')`"
params:
  country: Brazil 
---

<!-- Multiple parameters -->
---
title: "Investment Report for Projects in `r params$country`"
output: 
  html_document:
    toc: true
    toc_float: true
date: "`r format(Sys.time(), '%d %B %Y')`"
params:
  country: Brazil
  fy: 2018
  year_start: 2017-07-01
  year_end: 2018-06-30
---

```{r country-annual-investment-projects}
country_annual_investment_projects <- investment_services_projects %>%
  filter(country == params$country,
         date_disclosed >= params$year_start,
         date_disclosed <= params$year_end) 

ggplot(country_annual_investment_projects, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  ) 
```

<!-- Customising the report with CSS -->
<!-- Code added after the YAML header -->
<style>
  
#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px;
  border-color: #708090;
}

#header {
  color: #F08080;
  background-color: #F5F5F5;
  opacity: 0.6;
  font-family: Calibri;
  font-size: 20px;
}
  
body {
  color: #708090;
  font-family: Calibri;
  background-color: #F5F5F5;
}

pre {
  color: #708090;
  background-color: #F8F8FF;
}

</style>

<!-- Referencing the CSS file within the YAML header -->
---
title: "Investment Report for Projects in `r params$country`"
output: 
  html_document:
    css: styles.css
    toc: true
    toc_float: true
date: "`r format(Sys.time(), '%d %B %Y')`"
params:
  country: Brazil
  year_start: 2017-07-01
  year_end: 2018-06-30
  fy: 2018
---
