<!-- Analyzing data -->

<!-- Filtering for a particular country -->
---
title: "Investment Report"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---
<!-- Include the packages within the first chunk of code -->
```{r data, include = FALSE}
library(readr)
library(dplyr) 

investment_annual_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/d0251f26117bbcf0ea96ac276555b9003f4f7372/investment_annual_summary.csv")
investment_services_projects <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/bcb2e39ecbe521f4b414a21e35f7b8b5c50aec64/investment_services_projects.csv")
```


## Datasets 

### Investment Annual Summary

The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each region for each fiscal year, from 2012 to 2018.
```{r investment-annual-summary}
investment_annual_summary
```

### Investment Projects in Brazil

The `investment_services_projects` dataset provides information about each investment project from 2012 to 2018. Information listed includes the project name, company name, sector, project status, and investment amounts.
<!-- The label after r in the {} provides a label for this code chunk output -->
```{r brazil-investment-projects}
brazil_investment_projects <- investment_services_projects %>%
  filter(country == 'Brazil')

brazil_investment_projects
```


<!-- Filter by the fiscal year 
Fiscal year 2018 = 01Jul2017 - 30Jun2018
-->

### Investment Projects in Brazil in 2018

```{r brazil-investment-projects-2018}
brazil_investment_projects_2018 <- investment_services_projects %>%
  filter(country == "Brazil",
         date_disclosed >= '2017-07-01',
         date_disclosed <= '2018-06-30') 

brazil_investment_projects_2018
```

<!-- Referencing code within the markdown file -->
### Investment Projects in Brazil in 2018

```{r brazil-investment-projects-2018}
brazil_investment_projects_2018 <- investment_services_projects %>%
  filter(country == "Brazil",
         date_disclosed >= "2017-07-01",
         date_disclosed <= "2018-06-30") 

brazil_investment_projects_2018

brazil_investment_projects_2018_total <- brazil_investment_projects_2018 %>%
  summarize(sum_total_investment = sum(total_investment, na.rm = TRUE)) 
```

<!-- To include a dynamic output the backticks and r need to be included within the text. Should the underlying data change then the code 
updates the text as well. 
-->
The total investment amount for all projects in Brazil in the 2018 fiscal year was `r brazil_investment_projects_2018_total` million dollars.

<!-- Including plots -->
library(ggplot2)

### Investment Annual Summary

The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each region for each fiscal year, from 2012 to 2018.
```{r investment-annual-summary}
ggplot(investment_annual_summary, aes(x=fiscal_year, y=dollars_in_millions, color=region)) +
  geom_line() +
  labs(
    title = "Investment Annual Summary",
    x = "Fiscal Year",
    y = "Dollars in Millions"
  )


<!-- Setting chunk options to adjust the plots within the markdown -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = "center", out.width = '80%', echo = TRUE)
```

<!-- Adding a caption to the figure -->
```{r investment-annual-summary, out.width = '85%', fig.cap = 'Figure 1.1 The Investment Annual Summary for each region for 2012 to 2018'}
ggplot(investment_annual_summary, aes(x = fiscal_year, y = dollars_in_millions, color = region)) +
  geom_line() +
  labs(
    title = "Investment Annual Summary",
    x = "Fiscal Year",
    y = "Dollars in Millions"
  )
```
