<!-- Analyzing data -->

<!-- Filtering for a particular country -->
---
title: "Investment Report"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---
<!-- Include the packages within the first chunk of code -->
```{r data, include = FALSE}
library(readr)
library(dplyr) 

investment_annual_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/d0251f26117bbcf0ea96ac276555b9003f4f7372/investment_annual_summary.csv")
investment_services_projects <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/bcb2e39ecbe521f4b414a21e35f7b8b5c50aec64/investment_services_projects.csv")
```


## Datasets 

### Investment Annual Summary

The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each region for each fiscal year, from 2012 to 2018.
```{r investment-annual-summary}
investment_annual_summary
```

### Investment Projects in Brazil

The `investment_services_projects` dataset provides information about each investment project from 2012 to 2018. Information listed includes the project name, company name, sector, project status, and investment amounts.
<!-- The label after r in the {} provides a label for this code chunk output -->
```{r brazil-investment-projects}
brazil_investment_projects <- investment_services_projects %>%
  filter(country == 'Brazil')

brazil_investment_projects
```


